Liptschiz

### 2024-02-20 lipschitz/valabstraction.tex
add formula
test plots

>>>>

\subsubsection*{Constraints for $\gamma$}

We could get the following constraints for $\gamma$, using $y_i$ and $\hat{y}_i$ to denote the $x_i-x_i'$ and $\hat{x}_i-\hat{x}_i'$:\begin{align*}
	\hat{y}_i \leq a \gamma_i \hspace*{2ex} &\wedge \hspace*{2ex}\hat{y} \geq y_i - a \gamma_i\\
	\hat{y}_i \geq (a-1) \gamma_i  \hspace*{2ex} &\wedge \hspace*{2ex} \hat{y} \leq y_i + (1-a) \gamma_i,
\end{align*} where $a$ is a binary variable, $\gamma_i$ is the upper bound of $x_i-\hat{x}_i$.

\begin{tikzpicture}[
	declare function={
		f(\x,\y)=max((\x+\y),0)-max(\x,0);
	}]
	\begin{axis}[axis lines=center,
		axis on top,
		set layers=default,
		xrange=-3:3,
		yrange=-2:2,
		unit vector ratio=1 1 1,% <- HERE (taken from Phelype Oleinik's deleted answer)
		scale=3 %<- added to compensate for the downscaling
		% resulting from unit vector ratio=1 1 1
		]
		\addplot3[
		domain=-3:3,
		domain y=-1:1,
		samples=40,
		samples y=40,
		surf,
		] {f(\x,\y)};
	\end{axis}
\end{tikzpicture}
